---
title: "Alcohol vs Seat choice"
author: "Anthony Benitez"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
There are a lot of differences in each of the medians such like the front is 0, middle is 2, and the back is 5. 
  
### get fancy  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

Looking at the means of each seats like the back's mean is 9.6, front is 1.8, the middle is 3.2.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The pr percentage seems to small for it to mean that the ones in the back don't drink as much as its lead on to be the number is 0.000116.
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

The ones that are passed the dotted line means that they are similar so that means middle front are the same , middle back and front back are not the same. There is a 95% confidence level 

## Conclusions
The conclusion is that we have noticed that there at least two rows that are similar.

